---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(dplyr)
library(glue)
library(tibble)
library(tidyr)
```

# nflendzoneData

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This repository holds automated data releases for the `nflendzone` project (all data is published via GitHub Actions and GitHub Releases).

## Usage

You can download data hosted here directly from the [releases page](https://github.com/TyleerPollard410/nflendzoneData/releases) or programmatically via your own R functions.

## Automation Status

The following table shows the current status and last update of all automated data releases.

```{r automation-status-table, echo=FALSE, message=FALSE, warning=FALSE}
# ---- List your data tags here ----
tags <- tribble(
  ~tag,           ~caption,                   ~workflow_yaml,
  "scores",       "Game scores (all years)",  "update_scores.yml",
  "standings",    "Season standings",         "update_standings.yml"
  # Add more datasets/tags as needed!
)

# Function to build badge URL for each tag
badge_url <- function(tag) {
  url <- glue("https://github.com/TylerPollard410/nflendzoneData/releases/download/{tag}/timestamp.json")
  glue("[![{tag}](https://img.shields.io/badge/dynamic/json?color=blue&label=Last%20Updated&query=last_updated&style=flat-square&url={url})](https://github.com/TylerPollard410/nflendzoneData/releases/tag/{tag})")
}

# Function to build workflow badge for each tag
workflow_badge <- function(workflow_yaml, tag) {
  glue("![status](https://img.shields.io/github/actions/workflow/status/TylerPollard410/nflendzoneData/{workflow_yaml}?label={tag}_status&style=flat-square)")
}

status_tbl <- tags |>
  mutate(
    Status = workflow_badge(workflow_yaml, tag),
    `Last Updated` = badge_url(tag)
  ) |>
  select(Dataset = tag, Description = caption, Status, `Last Updated`)

knitr::kable(status_tbl, caption = "Automation status of all data releases. Click the 'Last Updated' badge to view the release for each dataset.")
```

---

## About Each Data Release

* **scores:** Contains final and in-progress scores for every game since 2006.
  *Data release*: The `.parquet` and `.rds` files are updated weekly during the season and after each round of games.
* **standings:** Aggregated standings, win/loss/tie records by season and division.
  *Data release*: Standings are updated every week after all games have concluded.

<!-- Repeat or update for each of your tags/datasets. Update the captions above as needed for each tag. -->

---

## How to Customize Tag Captions

In the status table code chunk, edit the `caption` for each tag to briefly explain what’s in that dataset/tag, e.g.:

* `"scores", "Game scores (all years)", ...`
* `"model_predictions", "Model output and forecasts", ...`
* `"weekly_props", "Player prop data, weekly", ...`

Use a clear, concise phrase.
**The best captions:**

* Identify data type, granularity, or special purpose (e.g., "Full-season EPA summaries" or "Play-by-play with advanced metrics").

---

## Programmatic Access Example (optional)

```r
# Example R code to download the latest scores file:
download.file(
  url = "https://github.com/TylerPollard410/nflendzoneData/releases/download/scores/scores_2024.rds",
  destfile = "scores_2024.rds"
)
```

---

# License

Data and code in this repo are released under the MIT License (or specify your own license).

## Code of Conduct

Please note that the nflendzoneData project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
